Illuminating a Dark Lens : A Type Ia Supernova \\ Magnified by the Galaxy Cluster Abell 2744

### 2015-05-18 TABLE/magnifications2.tex
added latest CATSv2 models, using Wang'15 spec-z and MI lists

Lam(v2)        & 10 &  32 & 5 & 5  &  \citealt{Lam:2014} & Updated version of the {\tt WSLAP+} model, using more selective strong-lensing constraints and GALFIT\tablenotemark{n} models for galaxy mass.

@@

\begin{deluxetable}{p{0.62in}ccc}
\tablecolumns{4}
\tablecaption{Lens model predictions for SN \tomas\ magnification\label{tab:PredictedMagnifications}}
\tablehead{ \colhead{Model\tablenotemark{a}} & 
            \colhead{Best\tablenotemark{b}} & \colhead{Median\tablenotemark{c}} & 
            \colhead{68\% Conf. Range\tablenotemark{d}}}
\startdata
Bradac(v1)      & 3.19     & 2.48  &   2.31$-$2.66 \\
CATS(v1)        & 2.28     & 2.29  &   2.25$-$2.34 \\
CATS(v1sw)      & \nodata  & 2.62  &   2.44$-$2.80 \\
Merten          & 2.33     & 2.24  &   2.04$-$2.92 \\
Sharon(v1)      & 2.56     & 2.60  &   2.44$-$2.78 \\
Sharon(v2)      & 2.74     & 2.59  &   2.42$-$2.85 \\
Zitrin-LTM      & 2.67     & 2.99  &   2.61$-$3.77 \\
Zitrin-NFW      & 2.09     & 2.29  &   2.07$-$2.52 \\
Williams        & 2.70     & 2.81  &   1.65$-$5.54 \\[0.1em]
\tableline\\[-0.5em]
CATS(v2)        & \nodata  & 3.42  &   3.27$-$3.58 \\
Diego           &  \nodata  & 1.80  &   1.44$-$2.16 \\
GLAFIC          & 2.34     & 2.29  &   2.19$-$2.37 \\
Lam(v1)         & \nodata  & 2.79  &   2.42$-$3.16 \\[0.5em]
Bradac(v2)$^{\rm *}$ & 2.23     & 2.26  &   2.30$-$2.23 \\
Lam(v2)$^{\rm *}$ & 1.86     & 1.91  &   1.54$-$2.28
\enddata
\tablenotetext{a}{Models above the line are from the pre-HFF set, and those below incorporate HFF data. The final two, marked by an asterisk, were not part of the blind test as they include modifications made after the measured magnification of the SN was known.}  
\tablenotetext{b}{The magnification returned for the optimal version of each model, as independently defined by each lens modeling team.}  
\tablenotetext{c}{Median magnification from 100-600 Monte Carlo realizations of the model.}  
\tablenotetext{d}{Confidence ranges about the median, enclosing 68\%\ of the realized values.}
\end{deluxetable}

>>>>

Lam(v2)        & 10 &  32 & 5 & 5  &  \citealt{Lam:2014} & Updated version of the {\tt WSLAP+} model, using more selective strong-lensing constraints and GALFIT\tablenotemark{n} models for galaxy mass.\\
CATS(v2.1)     & 50 & 151 & 7 & 18  &  \citealt{Jauzac:2014c} & Updated version of the CATSv2 model, adopting the spec-z constraints used for the Bradac(v2) model.\\
CATS(v2.2)     & 25 &  72 & 7 & 18  &  \citealt{Jauzac:2014c} & Updated version of the CATSv2 model, adopting the spec-z constraints and multiple-image definitions used for the Bradac(v2) model.

@@

\begin{deluxetable}{p{0.62in}ccc}
\tablecolumns{4}
\tablecaption{Lens model predictions for SN \tomas\ magnification\label{tab:PredictedMagnifications}}
\tablehead{ \colhead{Model\tablenotemark{a}} & 
            \colhead{Best\tablenotemark{b}} & \colhead{Median\tablenotemark{c}} & 
            \colhead{68\% Conf. Range\tablenotemark{d}}}
\startdata
Bradac(v1)      & 3.19     & 2.48  &   2.31$-$2.66 \\
CATS(v1)        & 2.28     & 2.29  &   2.25$-$2.34 \\
CATS(v1sw)      & \nodata  & 2.62  &   2.44$-$2.80 \\
Merten          & 2.33     & 2.24  &   2.04$-$2.92 \\
Sharon(v1)      & 2.56     & 2.60  &   2.44$-$2.78 \\
Sharon(v2)      & 2.74     & 2.59  &   2.42$-$2.85 \\
Zitrin-LTM      & 2.67     & 2.99  &   2.61$-$3.77 \\
Zitrin-NFW      & 2.09     & 2.29  &   2.07$-$2.52 \\
Williams        & 2.70     & 2.81  &   1.65$-$5.54 \\[0.1em]
\tableline\\[-0.5em]
CATS(v2)        & \nodata  & 3.42  &   3.27$-$3.58 \\
Diego           &  \nodata  & 1.80  &   1.44$-$2.16 \\
GLAFIC          & 2.34     & 2.29  &   2.19$-$2.37 \\
Lam(v1)         & \nodata  & 2.79  &   2.42$-$3.16 \\[0.5em]
Bradac(v2)$^{\rm *}$ & 2.23     & 2.26  &   2.30$-$2.23 \\
Lam(v2)$^{\rm *}$ & 1.86     & 1.91  &   1.54$-$2.28\\
CATS(v2.1)$^{\rm *}$ & \nodata & 3.06  &   2.90$-$3.22 \\
CATS(v2.2)$^{\rm *}$ & \nodata & 3.07  &   2.92$-$3.24 \\
\enddata
\tablenotetext{a}{Models above the line are from the pre-HFF set, and those below incorporate HFF data. The final two, marked by an asterisk, were not part of the blind test as they include modifications made after the measured magnification of the SN was known.}  
\tablenotetext{b}{The magnification returned for the optimal version of each model, as independently defined by each lens modeling team.}  
\tablenotetext{c}{Median magnification from 100-600 Monte Carlo realizations of the model.}  
\tablenotetext{d}{Confidence ranges about the median, enclosing 68\%\ of the realized values.}
\end{deluxetable}

### 2015-05-18 snTomas.tex
tiny tweaks
added latest CATSv2 models, using Wang'15 spec-z and MI lists

\begin{abstract}
\changenote{Reduced to $<250$ words.}\\
SN \tomas\ is a Type Ia Supernova (SN) discovered at
$z=1.3457\pm0.0001$ behind the galaxy cluster Abell 2744
($z=0.308$). This SN 
%has a projected separation from the cluster core
%of $\sim$40\arcsec, 
is closer to the critical lensing line than any
previous cluster-lensed Type Ia SN, 
%As such, it provides 
providing a valuable
opportunity to test galaxy cluster lens models
with the direct measurement of an absolute magnification at the edge
of the strong-lensing region.  
%We derive a tightly constrained measure
%of the peak apparent magnitude, corrected for light curve shape and
%extinction.  
In a cosmology-independent analysis, we find that \tomas\ is
$0.77\pm0.15$ magnitudes brighter than unlensed Type Ia SNe at similar
redshift, implying a lensing magnification of 
$\mu_{\rm obs}=2.03\pm0.29$. 
\change{In future lens models of Abell 2744, this could
provide some leverage for breaking degeneracies that positional
constraints cannot disentangle.}  We compare the measured $\mu$
against predicted magnifications from 15 lens models, \change{ of
which 13 were generated before the SN magnification was known,
qualifying as a pure ``blind test.''}  The models are collectively
fairly accurate: \change{6 of the blind models and both of the post-SN
models} deliver median magnifications that are consistent with the
measured $\mu$ to within 1$\sigma$.  However, there is a subtle
systematic bias: all of the models that disagree with the SN $\mu$ 
%by more than $1\sigma$ 
are {\it higher} than the measured value and 6 of these
are $\geq1.5\sigma$ above the measured magnification.  We
evaluate possible causes for this mild bias,
%and reject explanations
%that invoke misinterpretation of the SN data or errors in the
%definition of the lens models. We 
and find that
% -- at least for this
%cluster and this line of sight -- 
the most accurate models are those that employ stringent quality cuts
\change{and use a large fraction of spectroscopically measured 
redshifts of multiple images.}
% A more robust evaluation
%\change{Further examination} of systematic biases 
%could be achieved 
%\change{could be pursued with more}
%lens model comparisons using lensed
%Type Ia SNe, as well as cluster lensing simulations.
\end{abstract}

@@

Table~\ref{tab:PredictedMagnifications} gives each model's predicted
magnification and uncertainty for a source at $z=1.3457$ and at the
position of \tomas.  
\changeG{For thirteen of these models the SN magnification qualifies as a true
``blind test'', as they were completed before the SN \tomas\
magnification measurement was known.  The final two models (Bradac-v2
and Lam-v2) are technically not blind, although none of these modelers
used the SN magnification as a constraint, and the modelers did not
have access to the final SN magnification value when constructing
their model.}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{FIG/snTomas_magnifications}
\caption{ 
Comparison of the observed lensing magnification to predictions from
lens models. The vertical blue line shows the constraints from
SN \tomas\ derived in Section~\ref{sec:DistanceAndMagnification} using
the MLCS2k2 fitter, with a shaded region marking the total
uncertainty. Markers with horizontal error bars show the median
magnification and 68\%\ confidence region from each of the 15 lensing
models.  Circles indicate models that use only strong-lensing
constraints, while diamonds denote those that also incorporate
weak-lensing measurements.  \change{Models using a ``free-form''
approach are shown as open markers, while those in the ``parametric''
family are given filled markers.  The top half, with points in black, shows the nine
models that were constructed using only data available before the
start of the Frontier Fields observations. A black dashed line marks the
unweighted mean for these models, at $\mu=2.6$.
The lower six models in
green used additional input constraints, including new multiply imaged
systems and redshifts.  The final two points, with square orange
outlines, are the ``unblind'' models that were generated after the
magnification of the SN was known.  
The green dashed line marks the
unweighted mean for these six models, at $\mu=2.3$.
\label{fig:LensingTest} }}
\end{center}
\end{figure}

In Figure~\ref{fig:LensingTest} the model predictions are plotted
alongside the observed magnification of SN \tomas, derived in
Section~\ref{sec:DistanceAndMagnification}.  To first order, this
comparison shows that these 15 models are largely consistent with each
other and with the observed magnification of SN \tomas. \change{If we
take the first set of 9 pre-HFF models and naively treat each as an
independent prediction for the magnification (they are not all
independent) and if we ignore their quoted uncertainties, we would get
an unweighted mean for the pre-HFF sample of $\mu_{\rm
pre}=2.6\pm0.4$.  This is separated from the observed SN magnification
by $\delta\mu/\mu=28\%$, which is approximately a 1.5$\sigma$
difference. The addition of deeper imaging and new spectroscopic
constraints from the HFF program and affiliated efforts should be
expected to improve the lens models, and in
Figure~\ref{fig:LensingTest} we see that it does: the mean for the
post-HFF sample is $\mu_{\rm post}=2.3\pm0.6$, fully consistent with
the observed SN magnification.}

%Figure~\ref{fig:LensingTest} also separates the models based on the
%scope of input data constraints used.  Ten of the models rely only on
%strong-lensing constraints (plotted as circles), while the other four
%also use weak-lensing measurements (diamonds).

This is largely in agreement with the results
of \citetalias{Patel:2014} and \citet{Nordin:2014}, \change{where
model predictions were found to be in reasonably good agreement with a
set of 3 lensed SNe from the CLASH program.  The general agreement
between the model predictions and the SN measurement} is especially
encouraging for these Abell 2744 models. This is a merging cluster
with a complex mass distribution, and \change{the SN is located
outside of the strong-lensing region where the models are most tightly
constrained.}

@@

\subsubsection{Misidentification of a multiple image}
\citet{Jauzac:2014c} proposed a correction
for the location of image 3.3, the third component of a triply-imaged
galaxy \citep{Merten:2011} at $z=3.98\pm0.02$ \citep{Johnson:2014}.
This possibly specious multiple image is only $\sim$10\arcsec\ from
the SN \tomas\ position, meaning a change in its location could have a
large impact on the predicted magnification for
SN \tomas\ \citep[see][for a quantitative discussion of this
effect]{Johnson:2014}.  However, \citet{Jauzac:2014c} also evaluated a
version of the CATS(v2) model in which this single source is left in
the original position and found that the location of image 3.3 does
not significantly affect the predicted magnifications.  Furthermore,
dividing our 15 models into those using the original location vs those
that adopt the new position, we find that both groups include models
that are within 1$\sigma$ of the observed $\mu$ as well as
significantly discrepant points.

@@

\change{ Of the 15 models examined here, both of the Zitrin models 
follow the first strategy, using image-plane optimization.  The
Zitrin-LTM model delivers a significantly discrepant magnification,
while the Zitrin-NFW latter is within 1$\sigma$ of the SN
magnification.  The Diego model uses the second strategy of restricted
source-plane minimization, and reports a magnification very close to
the measured value.  The CATS(v2) model is the most extreme example of
the final strategy, as it incorporates more multiply-imaged sources
over a wider redshift range than any other model. However, this model
is also the most discrepant, with a predicted $\mu$ that is $>4\sigma$
from the SN magnification.  Thus, the results from this simplistic
model comparison are mixed.  We therefore cannot conclude that source
plane minimization alone is the root cause of the observed systematic
bias. }

@@

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{FIG/tension}
\caption{ \label{fig:Nspecz}
The model tension as a function of strong-lensing constraints. The y
axis in both panels marks the number of standard deviations in
discrepancy between the measured SN magnification and the prediction
from each lens model. The left panel plots this tension against the
total number of multiply imaged systems used, and the right panel
plots the fraction of
multiply-imaged systems that have a spectroscopic redshift
constraint.  Marker shapes and colors are the same as in
Figure~\ref{fig:LensingTest}.}
\end{center}
\end{figure*}

\change{
Increasing the number of multiply imaged galaxies used as
strong-lensing constraints should in principle lead to improvements in
the accuracy and precision of magnification predictions.  We have
already seen some suggestion of this from
Figure~\ref{fig:LensingTest}, which shows that the post-HFF models are
collectively better than the pre-HFF models at predicting the
SN \tomas\ magnification.  
The left panel of Figure~\ref{fig:Nspecz} isolates this variable by
plotting the tension between each model prediction and the measured SN
magnification against the number of multiply-imaged galaxies used as
strong-lensing constraints. There is no clear correlation here, and in
fact the most significant outlier (CATS(v2)) is actually the one using
the most multiply-imaged systems.  
}

\change{
In the right panel of Figure~\ref{fig:Nspecz} we examine an
alternative explanation by plotting the model tension against the
fraction of strong-lensing constraints that have a spectroscopic
redshift. Here we see evidence for a correlation between model
accuracy and the fraction of multiply-imaged galaxies with
spectroscopic redshifts.  The apparent correlation is anchored on one
end by the low spectroscopic fraction and high tension for the
CATS(v2) model. At the other end we find two of the most accurate lens
models (Bradac(v2) and Lam(v2)), which both have a high spec-$z$
fraction and low tension.}

\change{
Of course this is not direct causation.  Consider the limit of just a
single multiply-imaged galaxy constraint: the spec-$z$ fraction could
be 1.0 but the model would be wildly unconstrained.  Rather, the
spec-$z$ fraction here serves as a stand-in for how stringently the
strong-lensing constraints are defined in these models.  Erroneous
redshifts assigned to multiply-imaged systems lacking a spec-$z$ are especially
problematic for relatively low redshift background systems. At lower
redshifts, the model-derived deflection angle and magnification show a
more rapid variation with the redshift of the background galaxy than
for similarly positioned high redshift background galaxies}

The SN \tomas\ comparison therefore suggests that to get accurate
magnifications, lens models should employ a strict vetting of the
strong-lensing constraints.  Multiply-imaged systems should ideally
have spectroscopic redshifts, or at least very well constrained
photometric redshifts.  The {\it quality} of strong-lensing
constraints is perhaps just as important as the {\it quantity}.

It is relevant to note that the two models highlighted for their
accuracy here (Bradac(v2) and Lam(v2)) also happen to be the two
models that are not truly ``blind,'' in that the modelers were aware
of preliminary analysis of the SN magnification.  However, neither of
these models used the SN magnification as an input constraint, neither
were consciously tuned to match the SN magnification, and the modelers did not
have a final measurement of the SN magnification at the time their
models were generated.

@@

Taking advantage of the availability of 15 well-constrained lens
models for the Abell 2744 cluster, we have used SN \tomas\ to ask how
accurately these lens models can predict the magnification along this
line of sight.  We find that these models are consistent, and fairly
accurate, collectively predicting $\mu=2.5\pm0.4$, within 1$\sigma$ of
the measured value.  This is encouraging, and reinforces the quality
and value of these public lens models for studying magnified
background objects.  However, we note that all but two of the tested
models provide a median magnification prediction that is larger than
the measurement from the SN, and all the models with significant
discrepancy are too high.  This may be an indication that there is a
small systematic bias at work, at least in some of the models.

@@

Turning to the lens models, we have considered 4 ways in which a bias
might be introduced into the lens models:

\begin{enumerate}
\item Cosmic weak lensing 
\item Peculiar mass for a nearby cluster member
\item Cosmological parameter uncertainty
\item Misidentification of a multiple image
\item Source plane minimization
\end{enumerate}

>>>>

\begin{abstract}
\changenote{Reduced to $<250$ words.}\\
SN \tomas\ is a Type Ia Supernova (SN) discovered at
$z=1.3457\pm0.0001$ behind the galaxy cluster Abell 2744
($z=0.308$). This SN 
%has a projected separation from the cluster core
%of $\sim$40\arcsec, 
is closer to the critical lensing line than any
previous cluster-lensed Type Ia SN, 
%As such, it provides 
providing a valuable
opportunity to test galaxy cluster lens models
with the direct measurement of an absolute magnification at the edge
of the strong-lensing region.  
%We derive a tightly constrained measure
%of the peak apparent magnitude, corrected for light curve shape and
%extinction.  
In a cosmology-independent analysis, we find that \tomas\ is
$0.77\pm0.15$ magnitudes brighter than unlensed Type Ia SNe at similar
redshift, implying a lensing magnification of 
$\mu_{\rm obs}=2.03\pm0.29$. 
\change{In future lens models of Abell 2744, this could
provide some leverage for breaking degeneracies that positional
constraints cannot disentangle.}  We compare the measured $\mu$
against predicted magnifications from 17 lens models, \change{ of
which 13 were generated before the SN magnification was known,
qualifying as a pure ``blind test.''}  The models are collectively
fairly accurate: 8 of the models deliver median magnifications that
are consistent with the measured $\mu$ to within 1$\sigma$.  However,
there is a subtle systematic bias: all of the models that disagree
with the SN $\mu$
%by more than $1\sigma$ 
are {\it higher} than the measured value and 6 of these
are $\geq1.5\sigma$ above the measured magnification.  We
evaluate possible causes for this mild bias,
%and reject explanations
%that invoke misinterpretation of the SN data or errors in the
%definition of the lens models. We 
and find that
% -- at least for this
%cluster and this line of sight -- 
the most accurate models are those that employ stringent quality cuts
\change{and use a large fraction of spectroscopically measured 
redshifts of multiple images.}
% A more robust evaluation
%\change{Further examination} of systematic biases 
%could be achieved 
%\change{could be pursued with more}
%lens model comparisons using lensed
%Type Ia SNe, as well as cluster lensing simulations.
\end{abstract}

@@

Table~\ref{tab:PredictedMagnifications} gives each model's predicted
magnification and uncertainty for a source at $z=1.3457$ and at the
position of \tomas.  
\changeG{For thirteen of these models the SN magnification qualifies as a true
``blind test'', as they were completed before the SN \tomas\
magnification measurement was known.  The final four models
(Bradac-v2, Lam-v2, CATSv2.1 and 2.2) are technically not blind,
although none of these modelers used the SN magnification as a
constraint, and the modelers did not have access to the final SN
magnification value when constructing their model.}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{FIG/snTomas_magnifications}
\caption{ 
Comparison of the observed lensing magnification to predictions from
lens models. The vertical blue line shows the constraints from
SN \tomas\ derived in Section~\ref{sec:DistanceAndMagnification} using
the MLCS2k2 fitter, with a shaded region marking the total
uncertainty. Markers with horizontal error bars show the median
magnification and 68\%\ confidence region from each of the 17 lensing
models.  Circles indicate models that use only strong-lensing
constraints, while diamonds denote those that also incorporate
weak-lensing measurements.  \change{Models using a ``free-form''
approach are shown as open markers, while those in the ``parametric''
family are given filled markers.  The top half, with points in black, shows the nine
models that were constructed using only data available before the
start of the Frontier Fields observations. A black dashed line marks the
unweighted mean for these models, at $\mu=2.6$.
The lower six models in
green used additional input constraints, including new multiply imaged
systems and redshifts.  The final two points, with square orange
outlines, are the ``unblind'' models that were generated after the
magnification of the SN was known.  
The green dashed line marks the
unweighted mean for these six models, at $\mu=2.3$.
\label{fig:LensingTest} }}
\end{center}
\end{figure}

In Figure~\ref{fig:LensingTest} the model predictions are plotted
alongside the observed magnification of SN \tomas, derived in
Section~\ref{sec:DistanceAndMagnification}.  To first order, this
comparison shows that these 17 models are largely consistent with each
other and with the observed magnification of SN \tomas. \change{ The
``naive mean'' of the full set of models is $\mu_{\rm pre}=2.6\pm0.4$.
This is an unweighted mean (i.e. we ignore all quoted uncertainties)
derived by naively treating each as an independent
prediction for the magnification (this is clearly incorrect, as
several models are represented multiple times as different versions).
The naive mean is separated from the observed SN magnification by
$\delta\mu/\mu=28\%$, which is approximately a 1.5$\sigma$ difference.}

\change{
This is approximately consistent with the results
of \citetalias{Patel:2014} and \citet{Nordin:2014}, where
model predictions were found to be in reasonably good agreement with a
set of 3 lensed SNe from the CLASH program.  The general agreement
between the model predictions and the SN measurement is especially
encouraging for these Abell 2744 models. This is a merging cluster
with a complex mass distribution, and the SN is located
outside of the strong-lensing region where the models are most tightly
constrained.}

@@

\subsubsection{Misidentification of a multiple image}
\citet{Jauzac:2014c} proposed a correction
for the location of image 3.3, the third component of a triply-imaged
galaxy \citep{Merten:2011} at $z=3.98\pm0.02$ \citep{Johnson:2014}.
This possibly specious multiple image is only $\sim$10\arcsec\ from
the SN \tomas\ position, meaning a change in its location could have a
large impact on the predicted magnification for
SN \tomas\ \citep[see][for a quantitative discussion of this
effect]{Johnson:2014}.  However, \citet{Jauzac:2014c} also evaluated a
version of the CATS(v2) model in which this single source is left in
the original position and found that the location of image 3.3 does
not significantly affect the predicted magnifications.  Furthermore,
dividing our 17 models into those using the original location vs those
that adopt the new position, we find that both groups include models
that are within 1$\sigma$ of the observed $\mu$ as well as
significantly discrepant points.

@@

\change{ Of the 17 models examined here, both of the Zitrin models 
follow the first strategy, using image-plane optimization.  The
Zitrin-LTM model delivers a significantly discrepant magnification,
while the Zitrin-NFW latter is within 1$\sigma$ of the SN
magnification.  The Diego model uses the second strategy of restricted
source-plane minimization, and reports a magnification very close to
the measured value.  The CATS(v2) model is the most extreme example of
the final strategy, as it incorporates more multiply-imaged sources
over a wider redshift range than any other model. However, this model
is also the most discrepant, with a predicted $\mu$ that is $>4\sigma$
from the SN magnification.  Thus, the results from this simplistic
model comparison are mixed.  We therefore cannot conclude that source
plane minimization alone is the root cause of the observed systematic
bias. }

@@

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{FIG/tension}
\caption{ \label{fig:Nspecz}
The model tension as a function of strong-lensing constraints. The y
axis in both panels marks the number of standard deviations in
discrepancy between the measured SN magnification and the prediction
from each lens model. The left panel plots this tension against the
total number of multiply imaged systems used, and the right panel
plots the fraction of
multiply-imaged systems that have a spectroscopic redshift
constraint.  Marker shapes and colors are the same as in
Figure~\ref{fig:LensingTest}.  \change{In both panels, three lens model sequences are highlighted with connecting lines: the Bradac, Lam, and CATS(v2) models, which are the three examples where the quantity and quality of strong lensing constraints changed substantially from one model version to the next.}
} 
\end{center}
\end{figure*}

\change{
The addition of deeper imaging and new spectroscopic constraints from
the HFF program and affiliated efforts might be expected to improve
the accuracy of magnification predictions. However, in
Figure~\ref{fig:LensingTest} we saw no evidence for a universal
improvement in model accuracy when moving from the pre- to the
post-HFF models.  In Figure~\ref{fig:Nspecz} we attempt to refine this
hypothesis by isolating the quantity and quality of strong lensing constraints. 
}

\change{
The left panel plots the tension between each model prediction and the
measured SN magnification against the number of multiply-imaged
galaxies used as strong-lensing constraints. The Bradac, Lam and
CATSv2 model series are highlighted here with connecting lines, as
three examples where the number of systems used has changed
substantially from one version to the next, but the model construction
has remained fundamentally unchanged.
There is no clear correlation here, and in
fact for both the Lam and CATSv2 model series, we see the tension
actually {\it increases} for a larger number of strong-lensing constraints.}

\change{
In the right panel of Figure~\ref{fig:Nspecz} we examine an
alternative explanation by plotting the model tension against the
fraction of strong-lensing constraints that have a spectroscopic
redshift. Here we see that all three of the testable model series
(Bradac,Lam,CATSv2) become {\it more} accurate as the spec-z fraction
increases.\footnote{Of course this apparent correlation does not imply
any direct causation. Consider the limit of just a single
multiply-imaged galaxy constraint: the spec-$z$ fraction could be 1.0
but the model would be wildly unconstrained.}  The spec-$z$ fraction
here serves as a crude stand-in for measuring how
stringently the strong-lensing constraints are selected in these
models.
}

\change{
The SN \tomas\ comparison therefore supports the notion that the {\it
quality} of strong-lensing constraints is just as important as the
{\it quantity}.  To get accurate magnifications, lens models should
employ a strict vetting of the multiply-imaged systems.  Each system
used should ideally have a spectroscopic redshift, or at least a very
well constrained photometric redshift.  The primary value in this
strict vetting is to avoid erroneous redshifts being assigned to
multiply-imaged systems that are unconstrained in redshift space.
Such redshift errors are especially problematic for relatively low-$z$
background systems: at lower redshifts the model-derived deflection
angle and magnification show a more rapid variation with the redshift
of the background galaxy than for similarly positioned high redshift
galaxies.}

It is relevant to note that the three model series highlighted here
(Bradac, CATSv2 and Lam) also happen to be the three models that are
not truly ``blind,'' in that the modelers were aware of preliminary
analysis of the SN magnification when constructing the latest version.
However, none of these models used the SN magnification as an input
constraint, and none were consciously tuned to match the SN
magnification. In fact, for the Bradac(v2) and Lam(v2) cases, the
modelers did not have access to a final measurement of the SN
magnification at the time their models were generated.

@@

Taking advantage of the availability of 17 well-constrained lens
models for the Abell 2744 cluster, we have used SN \tomas\ to ask how
accurately these lens models can predict the magnification along this
line of sight.  We find that these models are consistent, and fairly
accurate, collectively predicting $\mu=2.5\pm0.4$, within 1$\sigma$ of
the measured value.  This is encouraging, and reinforces the quality
and value of these public lens models for studying magnified
background objects.  However, we note that all but two of the tested
models provide a median magnification prediction that is larger than
the measurement from the SN, and all the models with significant
discrepancy are too high.  This may be an indication that there is a
small systematic bias at work, at least in some of the models.

@@

Turning to the lens models, we have considered 5 ways in which a bias
might be introduced into the lens models:

\begin{enumerate}
\item Cosmic weak lensing 
\item Peculiar mass for a nearby cluster member
\item Cosmological parameter uncertainty
\item Misidentification of a multiple image
\item \change{Source plane minimization}
\end{enumerate}
